Incentivizing Exploration by Heterogeneous Users

### 2018-02-06 algorithm.tex
partial edits on regret proof

With this additional notation, we now prove several lemmas.
First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.

Notation: $t_s$ is end time for phase $s$.

@@

Thus, for any phase $s \geq \EvenLaterPhase$
Algorithm~\ref{alg:basic-incentivizing} incentivizes any given arm $i$
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
the expected total number of arm incentivizations is at most
\begin{align*}
\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)}
& = O\left( \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right).
\end{align*}
\dkcomment{It seems like with our choice of $x$ (which may be
  unavoidable), we get quite large factors, in particular with the
  fourth power.
  Also, it would be nice if we could simplify the $\frac{1}{1-\exp()}$
  term. Unfortunately, I think that the inequality goes the wrong way
  for applying the standard $\exp(-x) \geq 1-x$ bound.}
\end{proof}

@@

\subsection{Bounding the Total Regret}
\dkcomment{Edited up to here so far.}

Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.

We use $R = \max_{\AgV, i,j} \AgV \cdot (u_i - u_j)$ to denote the
maximum regret that can be incurred at each time.
Assumption~\ref{A2} implies that the maximum regret or payment
incurred in any one round is finite.

@@

\begin{proof}
For regret incurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.

For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents. Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24\ARMNUM^2 d \frac{1}{\exp(\frac{1.8\delta_{0}}{64\Diam^2 d^2\sigma^2})-1} + Nn_1\right]R$.

For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
\begin{itemize}
\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round. For $k>t_{n+1}-t_{n}$, we define $\tau_{n}^{k}=\infty$. For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)\times R$. We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$. For $k>t_{n+1}-t_{n}$, we define $r_1(\tau_{n}^{k})=0$.
\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$. We denote the regret incurred by these agents as $r_2(t)$.
\end{itemize}

Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
\begin{align}
&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
=& \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right]. \label{chap5:equ:r1}
\end{align}
Since
\begin{align}
& E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})] \nonumber \\
= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty)+E[r_1(\tau_{n}^{k})|\tau_{n}^{k}=\infty]\times P(\tau_{n}^{k}=\infty)) \nonumber \\
= & \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty), \nonumber
\end{align}

>>>>

\dkcomment{Keeping this around for now.}
Notation: $t_s$ is end time for phase $s$.

@@

Thus, for any phase $s \geq \EvenLaterPhase$
Algorithm~\ref{alg:basic-incentivizing} incentivizes any given arm $i$
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
the expected total number of arm incentivizations is at most
\begin{align*}
\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)}
& = O\left( \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right).
\end{align*}
\dkcomment{It seems like with our choice of $x$ (which may be
  unavoidable), we get quite large factors, in particular with the
  fourth power.
  Also, it would be nice if we could simplify the $\frac{1}{1-\exp()}$
  term. Unfortunately, I think that the inequality goes the wrong way
  for applying the standard $\exp(-x) \geq 1-x$ bound.}

\dkcomment{I'm leaving in all the dependencies on ``constant''
  parameters for now. We can decide later which ones to absorb into
  big-$O$.}
\end{proof}

@@

\subsection{Bounding the Total Regret}
In bounding the total regret, because agents' types are from a compact
set by Assumption~\ref{A2}, the maximum regret in any one round is
bounded by a constant.
We use $\MAXR = \max_{\AgV, i,i'} \AgV \cdot (\ArmV{i} - \ArmV{i'})$
to denote this constant upper bound on the maximum regret that can be
incurred in any one time step.

@@

\begin{proof}
As before, let $\LatePhase = \max (50, \frac{92.16 \sigma^4}{x^4})$.
By Lemma~\ref{lem:phase-length}, each phase $s = 1, \ldots, \LatePhase$
in expectation lasts at most $\ARMNUM s$ steps,
so the total expected regret incurred in these phases is at most
$\sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s = O(\ARMNUM \MAXR \LatePhase^2)$.

Regret incurred after the first \LatePhase phases can arise in two ways:
(1) an agent was incentivized to pull a suboptimal arm, or
(2) an agent myopically pulled a suboptimal arm.
By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
incentivizes agents at most 
$O \left( \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right)$
times in expectation, each time causing regret at most \MAXR,
for a total expected regret of at most
$O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right)$.
For the rest of the proof, we focus on the regret incurred when agents
pull arms myopically and make mistakes.

We distinguish two types of agents, based on whether their preference
for their best arm over the second-best arm is ``large'' or ``small''.
To be more precise, we will define (with hindsight) a phase-dependent
cutoff $g(s)$, and for any agent type $\AgV \in \FirstTwo{i}{i'}$,
distinguish whether $\AgV \cdot (\ArmV{i} - \ArmV{i'}) \geq g(s)$ or not.

By Lemma~\ref{lem:sdelta}, the total measure of agents whose
preference is ``small'' in this sense is at most
$\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$ for all $\delta$.
\dkcomment{Put here whatever upper bound we use for these agents.}

\dkcomment{I edited up to this point. Some notation has been replaced
  below with query-replace, but not all of it.}

For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
\begin{itemize}
\item For those users whose utility difference between their best and
the second best arm is greater than $g(t)$:
we define a sequence of stopping time $\tau_{s}^{k}$ to be the \Kth{k}
time period in the \Kth{s} phase.
For $k > t_{s+1}-t_{s}$, we define $\tau_{s}^{k}=\infty$.
For $\tau_{s}^{k}=t$, the probability of these users making a mistake
is bounded above by
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$,
and the expected regret is bounded above by
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR$.
We denote the regret incurred by these agents by $r_1(\tau_{s}^{k})$.
For $k > t_{s+1}-t_{s}$, we define $r_1(\tau_{s}^{k})=0$.

\item For those user whose utility difference between their best and
the second best arm is smaller than $g(t)$:
this happens with probability \AlmostTied{g(t)} at each time,
and the regret is bounded above by
$\AlmostTied{g(t)} \cdot f(t) \leq \TieDensity f(t)^2$.
We denote the regret incurred by these agents as $r_2(t)$.
\end{itemize}

Thus, the cumulative expected regret incurred up to time $T$ when we
let the agent play myopically is bounded above by:
\begin{align}
\Expect{\sum_{t=1}^{T}r(t)} 
& = \Expect{\sum_{t=1}^{t_{\LatePhase}} r(t) + \sum_{t=t_{\LatePhase}}^{T}(r_1(t)+r_2(t))}  \nonumber \\
& \leq \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
     + \Expect{\sum_{s=\LatePhase}^{T}\sum_{t=t_{s}}^{t_{s+1}-1}r_1(t)}
     + \Expect{\sum_{t=1}^{T}r_2(t)} \nonumber \\
& = \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
     + \Expect{\sum_{s=\LatePhase}^{T} \sum_{k=1}^{\infty}r_1(\tau_{s}^{k})}
     + \Expect{\sum_{t=1}^{T}r_2(t)}. \label{chap5:equ:r1}
\end{align}
Since
\begin{align}
& E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})] \nonumber \\
= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty)+E[r_1(\tau_{n}^{k})|\tau_{n}^{k}=\infty]\times P(\tau_{n}^{k}=\infty)) \nonumber \\
= & \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty), \nonumber
\end{align}
